\subsection*{Discussion}

We present here a novel method for analysis of dMRI tractometry data that
relies on the Sparse Group Lasso \cite{simon2013sparse} to (a) make accurate
predictions of phenotypic properties of individual subjects while,
simultaneously, (b) identifying the features of the white matter that are
most important for this prediction in a completely data-driven approach. The
method is broadly applicable to a wide range of research questions: it
performs well in predicting both continuous variables, such as biological
age, as well as categorical variables, such as whether a person is a patient
or a healthy control. In both of these cases, SGL out-performs previous
algorithms that have been developed for these tasks
\cite{sarica2017corticospinal, Richard2018-ux, mcpherson2020single}. The
nested cross-validation approach used to fit the model and make both
predictions and inferences from the model guards against overfitting and
tunes the degree of sparseness required by the algorithm. This means that SGL
can accurately describe phenomena that are locally confined to a particular
anatomical location or diffusion property (e.g., FA in the CST) as well as
phenomena that are widely distributed amongst brain regions and measured
diffusion properties.

Specifically, we demonstrated that the algorithm correctly detects the fact
that ALS, which is a disease of lower motor neurons, is localized to the
cortico-spinal tract. This recapitulates the results of previous analysis of
these same data, using a targeted ROI-based approach
\cite{sarica2017corticospinal}. In contrast, for the analysis of biological
age, the coefficients identified by the algorithm are very widely distributed
across many parts of the white matter, mirroring previous results that show a
large and continuous distribution of life-span changes in white matter
properties \cite{yeatman2014lifespan}.

One drawback of our approach is also evident in the age regression results.
There are portions of the bundle profiles in
\cref{fig:age-results:wh-profile,fig:age-results:hbn-profile,fig:age-results:cc-profile}
for which the $\hat{\beta}$ coefficients are zero but for which the bundle
profiles clearly contain an age differentiating signal. While SGL correctly
identifies certain features as important, it is not guaranteed to identify
\emph{all} of the important features. It will identify a parsimonious set of
important features, dense enough to predict the phenotype and sparse enough
(at either the group or global level) to satisfy the sparsity constraints.

Taken together, these results demonstrate the promise of the
group-regularized regression approach. Even at the scale of dozens of
subjects, the results provided by SGL are both accurate, as well as
interpretable \cite{Murdoch2019-ax}: tractometry capitalizes on domain
knowledge to engineer meaningful features; SGL scores these features based on
their relative importance; enables a visualization of these feature
importance scores in the anatomical coordinate frame of the bundles (e.g.,
\cref{fig:class-results:coefs3d,fig:age-results:wh-coefs3d,fig:age-results:hbn-coefs3d,fig:age-results:cc-coefs3d})
and provides a means to understand model errors (e.g.,
\cref{fig:class-results:false-positives,fig:class-results:false-negatives}) .
Thus, this multivariate analysis approach both (a) achieves high
cross-validated accuracy for precision medicine applications of dMRI data and
(b) identifies relevant features of brain anatomy that can further our
neuroscientific understanding of clinical disorders.

Neuroscience has entered an era in which consortium efforts are amassing
large datasets of high-quality dMRI measurements to address a variety of
scientific questions \cite{jernigan2016ping, jernigan2018abcd,
alexander2017open, Miller2016-hw, VanEssen2012}. The volume and complexity of
these data pose a substantial challenge. Dimensionality reduction with
tractometry, followed by analysis with the approach we present here promises to
capitalize on the wealth of data and on the co-measurement of interesting and
important phenotypical data about brain health and about the participants'
cognitive abilities. We also expect the group-regularized approach to improve
with larger datasets.

SGL has many other potential applications in neuroscience, because
of the hierarchical and grouped nature of many data types that are
collected in multiple sample points within anatomically-defined areas.
For example, this method may be useful to understand the relationship
between fMRI recordings and behavior, where activity in each voxel
may co-vary with voxels within the same anatomical region and form
features and groups of features. Similarly, large-scale multi-electrode
recordings of neural activity in awake behaving animals are becoming
increasingly feasible \cite{steinmetz2018distributed, Jun2017-gv} and
these recordings can form features (neurons) and groups (neurons within
an anatomical region). More ambitiously perhaps, this approach may be
used to understand the role of correlations in so-called resting-state
fMRI time-series and behavior, where pairwise correlations between
voxels in different anatomical regions are features in the matrix and
features may be grouped by pairs of anatomical regions. Given the large
number of voxels in the surface of the gray matter and given that
correlations increase the number of features by a factor of $n^2$, this
would pose a challenging problem to solve using SGL.

The results we present here also motivate extensions of the method using more
sophisticated cost functions. For example, the fused sparse group lasso (FSGL)
\cite{zhou2012} extends SGL to enforce additional spatial structure: smoothness
in the variation of diffusion metrics along the bundles. As brain measurements
include additional structure (for example, bilateral symmetry), future work
could also incorporate overlapping group membership for each entry in the tract
profiles \cite{Rao2014-xm}. For example, a measurement could come from the
corpus callosum, but also from the right hemipshere. This would also require
extending the cost function used here to incorporate these constraints.
Similarly, unsupervised dimensionality reduction of tractometry data (e.g.,
\cite{Chamberland2019-mu}) could also benefit from constraints based on
grouping.

The method is packaged as open-source software called AFQ-Insight
that is openly available, and provides a clear API to allow
for extensions of the method. The sofware integrates within a
broader automated fiber quantification software ecosystem: AFQ
\cite{yeatman2012tract}, which extracts tractometry data from raw and
processed dMRI datasets, as well as AFQ-Browser, which visualizes
tractometry data and facilitates sharing of the results of dMRI studies
\cite{yeatman2018browser}. To facilitate reproducibility and ease use
of the software, the results presented
in this paper are also provided in
\url{https://github.com/richford/AFQ-Insight/tree/master/examples/preprint-notebooks} as a series of Jupyter notebooks
\cite{kluyver2016jupyter}.

